Contextuality and the Born rule in fuzzy quantum theories

### 2017-05-06 prop_letter.tex
prop_letter.tex \paragraph{Expectation Values for Quantum IVPMs} Updating...

\begin{table*}
\caption{\label{table:quantum-interval-expectation}This table highlights the
process to compute $\expval{\mathbf{O}_{1}}_{\bar{\mu}_{1}}$. Notice
that $\bar{\mu}_{1}$ is defined by Eq.~(\ref{eq:no-information-IVPM}),
$\mul_{1}$ and $\mur_{1}$ are defined by $\left[\mul_{1}\left(P\right),\mur_{1}\left(P\right)\right]=\bar{\mu}_{1}\left(P\right)$,
and $P_{3}^{+\prime}=\sum_{j\ge3}P_{j}^{s}=\mathbb{0}$. }

@@

\end{table*}
For example, given a three dimensional Hilbert space with an orthonormal
basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $. Let $J_{\mathrm{z}}=\proj{0}-\proj{2}$,
and $\mathbf{O}_{1}=2\mathbb{1}-J_{\mathrm{z}}^{2}=2\proj{1}+\proj{0}+\proj{2}$.
By following Table~\ref{table:quantum-interval-expectation}, we
have 
\begin{equation}
\expval{\mathbf{O}_{1}}_{\bar{\mu}_{1}}=\sum_{i=1}^{2}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]=\left[1,2\right]
\end{equation}
intuitively. Since two possible outcomes are $1$ and $2$, the expectation
value should be between them even if we no prior knowledge about the
likelihood of outcomes. In contrast, if we naively multiply eigenvalues
with intervals, their sum, $\sum_{i=1}^{2}\lambda_{i}^{+}\bar{\mu}_{1}\left(P_{i}^{+}\right)=\left[0,3\right]$,
is a worse estimation. In fact, estimating the lower-bound by $1\cdot0+2\cdot0=0$
is too pessimistic because we know one of outcomes must be happen
even without any prior knowledge.

Formally, the expectation value of an observable with respect to an
IVPM should be the minimum and maximum expectation value of the same
observable with respect to states consistent with it. We found this
is true when we require our IVPM to be convex, and on a commuting
sub-event space induced by an observable.

\begin{definition}
Given an observable~$\mathbf{O}$ with its spectrum decomposition~(\ref{eq:spectrum-decomposition}).
A set of projectors~$\events'\subseteq\events$ is called a sub-event
space induced by $\mathbf{O}$ if it is the minimal sub-event space
satisfying $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}\subseteq\events'$.
\end{definition}

\noindent Having this definitions, we can write down our idea formally
as follow.

\begin{thm}
Given a Hilbert space of $d\ge3$, for every quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
and any observable~$\mathbf{O}$ inducing a sub-event space~$\events'$,
if $\bar{\mu}$ is convex, then
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ .}\label{eq:quantum-interval-expectation-core}
\end{equation}
Conversely, if Eq.~(\ref{eq:quantum-interval-expectation-core})
holds for every observable, then $\bar{\mu}$ is convex.
\end{thm}

>>>>

\begin{table*}
\caption{\label{table:quantum-interval-expectation}This table highlights the
process to compute $\expval{\mathbf{O}_{1}}_{\bar{\mu}_{1}}$. Notice
that $\bar{\mu}_{1}$ is defined by Eq.~(\ref{eq:no-information-IVPM}),
$\mul_{1}$ and $\mur_{1}$ are defined by $\left[\mul_{1}\left(P\right),\mur_{1}\left(P\right)\right]=\bar{\mu}_{1}\left(P\right)$,
and $P_{3}^{+\prime}=\sum_{j\ge3}P_{j}^{s}=\mathbb{0}$ so that $\mul_{1}\left(P_{3}^{+\prime}\right)=\mur_{1}\left(P_{3}^{+\prime}\right)=0$.}

@@

\end{table*}
For example, given a three dimensional Hilbert space with an orthonormal
basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $. Let $J_{\mathrm{z}}=\proj{0}-\proj{2}$,
and $\mathbf{O}_{1}=2\mathbb{1}-J_{\mathrm{z}}^{2}=2\proj{1}+\proj{0}+\proj{2}$.
By following Table~\ref{table:quantum-interval-expectation}, we
have 
\begin{equation}
\expval{\mathbf{O}_{1}}_{\bar{\mu}_{1}}=\sum_{i=1}^{2}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]=\left[1,2\right]\textrm{ .}
\end{equation}
The expectation value is intuitively between two possible outcomes,
$1$ and $2$, even if we have no prior knowledge about the likelihood
of outcomes. In contrast, if we naively multiply eigenvalues with
intervals, their sum, $\sum_{i=1}^{2}\lambda_{i}^{+}\bar{\mu}_{1}\left(P_{i}^{+}\right)=\left[0,3\right]$,
is a worse and counter-intuitive estimation. In fact, estimating the
lower-bound by $1\cdot0+2\cdot0=0$ is too pessimistic because we
know one of outcomes must happen without any prior knowledge.

Formally, the expectation value of an observable with respect to an
IVPM should be the minimum and maximum expectation value of the same
observable with respect to states consistent with it. This is true
when we require our IVPM to be convex, and on a commuting sub-event
space induced by an observable.

\begin{definition}Given an observable~$\mathbf{O}$ with its spectrum
decomposition~(\ref{eq:spectrum-decomposition}). A set of projectors~$\events'\subseteq\events$
is called a sub-event space induced by $\mathbf{O}$ if it is the
minimal sub-event space containing $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}$.\end{definition}

\begin{thm}Given a Hilbert space of $d\ge3$, for every quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
and any observable~$\mathbf{O}$ inducing a sub-event space~$\events'$,
if $\bar{\mu}$ is convex, then
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ .}\label{eq:quantum-interval-expectation-core}
\end{equation}
Conversely, if Eq.~(\ref{eq:quantum-interval-expectation-core})
holds for every observable, then $\bar{\mu}$ is convex.\end{thm}
